---
title: "Randomization test for weighted mean tolerance values"
author: "Frank"
date: "`r format(Sys.Date())`"
output: github_document

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8)
```

```{css, echo=FALSE}
h1, h4 {
  text-align: center;
  color: black;
  font-weight: bold;
}
```

## Introduction

This is sample report for a randomization test on the weighted mean tolerance values of lost taxa in Red Run. Taxa include all families, orders, and genera. However, Chironomidae and Oligochaeta were excluded due to taxonomic bias and high abundance. 

```{r import excel file,warning=FALSE}
library(readxl)
b1wtv <- read_excel("C:/Users/tiena/OneDrive - Towson University/Thesis stuff/Data Analysis/Part a (1987 vs 2009)/Lost and Gained/Randomization of weighted tolval/Data (no Chirae and Oligta).xlsx", 
                       sheet = "B1")
```

## Defining a function to sample and take means 

```{r function}
set.seed(1)
sample_stats <- function(df, n=23){
  df <- df[sample(1:nrow(df), n, replace=F),]
  mx1 <- sum(df$TV*df$Density)/sum(df$Density)
  return(c(mx1))
}
```

## Run it once just to see output

```{r run once,results='hide'}
(sample_stats(b1wtv))
```

## Run it 10,000 times

```{r 10k times,results='hide'}
results <- replicate(10000, sample_stats(b1wtv,n=23))
```

## Plot the results and calculate p-value

```{r,echo=F,message=F}
distri_H0 <- hist(results, breaks=50, plot=FALSE)
plot(distri_H0, col = "white", xlab = "", 
     main = "Approx. null distribution of weighted mean tolerance value of taxa lost at B1", 
     cex.lab = 1.5, cex.main = 1.5) # plot the null distribution
abline(v = 4.891894386, col = "red") # show the observed value

(pval_b1_lost <- sum(results <= 4.891894386) / 10000)
```

